---
title: "title"
author: "author"
date: "2025-09-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Libraries

install.packages("DT")

library(nycflights13)
library(plotly)
library(dplyr)
library(DT)

# Data import

airlines <- nycflights13::airlines
airports <- nycflights13::airports
flights <- nycflights13::flights
planes <- nycflights13::planes
weather <- nycflights13::weather

```

# Exercice dplyr

Count the number of records of planes and the sum of seats by company (display real name and not the code) and display it in a table


```{r dplyr}

# Use DT::datatable


```

# Exercice ggplot2

Plot in a stacked bar plot the repartition of manufactureur by company for the top 5 companies in term of number of flights in 2013.

```{r ggplot2, echo=FALSE}


```

# Exercice plotly

Plot the relationship between departure delay (dep_delay) and arrival delay (arr_delay) for flights from JFK airport and color points by company and add a regression line for each company 

```{r plotly, echo=FALSE}




```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
